\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-31 Paper/Paper.tex
revise abstract.

	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), and verify its feasibility. The MAAM uses optical coherence tomography (OCT) and color fundus images to diagnose ocular diseases. It simulates the decision-making process of ophthalmologists by deducing the disease from abnormities. The model is composed of the Abnormity Models, which identify 11 abnormities from OCT images and 8 abnormities from fundus images, and the Diagnosis Model, which diagnoses 12 diseases by integrating information from the Abnormity Models through a fusion mechanism. We also introduce the concept of codominant abnormities and diseases, providing more information for reference. The final model has a diagnosis accuracy of 89\%.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
		\caption{OCT Abnormities}
		\vspace{0.3cm}
		\label{fig:OCT_abnormities}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
		\caption{Fundus Abnormities}
		\vspace{0.3cm}
		\label{fig:fundus_abnormities}
	\end{figure}

@@

	The main goal of this study is to devise a novel model and verify its feasibility. The MAAM takes both OCT and fundus images as input. We integrate information from different sources by employing the fusion mechanism. Moreover, we use an abnormity-to-disease approach and simulate the decision-making process of ophthalmologists. We also introduced codominant abnormities and diseases, providing more information for reference. There is some room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model, etc.

>>>>

	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanics, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.pdf}
		\caption{OCT Abnormities \autocite{Duker_Waheed_Goldman_2022}}
		\vspace{0.3cm}
		\label{fig:OCT_abnormities}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/fundus_Abnormities.pdf}
		\caption{Fundus Abnormities \autocite{Wolf_Kirchhof_Reim_2006}}
		\vspace{0.3cm}
		\label{fig:fundus_abnormities}
	\end{figure}

@@

	The main goal of this study is to devise a novel model and verify its feasibility. The MAAM takes both OCT and fundus images as input. We integrate information from different sources by employing the fusion mechanism. Moreover, we deduce disease from abnormities and simulate the decision-making process of ophthalmologists. We also introduced codominant abnormities and diseases, providing more information for reference. As a result, the model breaks the black box of complex neural network and exposes more information. On the other hand, there is some room for improvement, such as gathering more authentic data, introducing the expertise of ophthalmologists, refining the Abnormity-to-Disease Deduction Criteria, and improving the structure of the Diagnosis Model, etc.
